Guilt, shame, and anti-war action in an authoritarian country at war

### 2023-04-27 manuscript.Rmd
Working version of reproducible manuscript

h1 <- 'cguiltf ~ demv+pcyn_ma+pcyn_im+pal+pr
ishamef ~ demv+pcyn_ma+pcyn_im+pal+pr
mshamef ~ demv+pcyn_ma+pcyn_im+pal+pr
demv~~pcyn_ma+pcyn_im+pal+pr
pcyn_ma~~pcyn_im+pal+pr
pcyn_im~~pal+pr
pal~~pr
'
fit <- sem(h1, data=d3, estimator="MLR")
summary(fit,fit.measures=TRUE, standardized=TRUE)
#only democratic values and belief that politicians are bad predict higher guilt and shame

@@

knitr::kable(table3_numbers, caption='Path model predicting group-based guilt and shame from political beliefs.', booktabs = TRUE, escape = FALSE) %>% 
  kableExtra::kable_styling(font_size = 8, latex_options = "HOLD_position")

>>>>

h1 <- 'cguiltf ~ demv+pcyn_ma+pcyn_im+pal+pr
ishamef ~ demv+pcyn_ma+pcyn_im+pal+pr
mshamef ~ demv+pcyn_ma+pcyn_im+pal+pr
demv~~pcyn_ma+pcyn_im+pal+pr
pcyn_ma~~pcyn_im+pal+pr
pcyn_im~~pal+pr
pal~~pr
'
fit <- sem(h1, data=d3, estimator="MLR")
S1data <- summary(fit,fit.measures=TRUE, standardized=TRUE)
#only democratic values and belief that politicians are bad predict higher guilt and shame

@@

tableS1_numbers <- matrix(0,nrow=18,ncol=5)
tableS1_numbers[c(2:6,8:12,14:18),1] <- round(S1data$pe$est[1:15],digits=2)
tableS1_numbers[c(2:6,8:12,14:18),2] <- round(S1data$pe$se[1:15],digits=2)
tableS1_numbers[c(2:6,8:12,14:18),3] <- round(S1data$pe$z[1:15],digits=2)
tableS1_numbers[c(2:6,8:12,14:18),4] <- round(S1data$pe$pvalue[1:15],digits=3)
tableS1_numbers[c(2:6,8:12,14:18),5] <- round(S1data$pe$std.all[1:15],digits=2)

tableS1_numbers[which(tableS1_numbers==0)] <- '<0.001'
tableS1_numbers[c(1,7,13),] <- ' '

rownames(tableS1_numbers) <- c("Guilt", "Democratic values", "Political cynicism (politicians)", "Political cynicism (politics)","Political alienation","Political responsibility","Image shame","Democratic values", "Political cynicism (politicians)", "Political cynicism (politics)","Political alienation","Political responsibility","Moral shame","Democratic values", "Political cynicism (politicians)", "Political cynicism (politics)","Political alienation","Political responsibility")

colnames(tableS1_numbers) <- c("b", "SE", "Z", "p", "$\\beta$")

knitr::kable(tableS1_numbers, caption='Path model predicting group-based guilt and shame from political beliefs.', align='rrrrr', booktabs = TRUE, escape = FALSE) %>% 
  kableExtra::kable_styling(font_size = 8, latex_options = "HOLD_position") %>%
  row_spec(0,italic=T) %>%
  row_spec(1,bold=T,italic=T) %>%
  row_spec(7,bold=T,italic=T) %>%
  row_spec(13,bold=T,italic=T)

### 2023-04-27 manuscript.tex
Working version of reproducible manuscript

\caption{\label{tab:TableS1}Path model predicting group-based guilt and shame from political beliefs.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{llllll}
\toprule
  & $\beta$ & b & SE & t-value & p\\
\midrule
Intercept & 0 & -0.1 & 0.12 & -0.82 & 0.410\\
Emotions: Positive & -0.032 & -0.03 & 0.03 & -0.96 & 0.337\\
Emotions: Negative Dominant & 0.237 & 0.19 & 0.03 & 6.4 & <0.001\\
Emotions: Negative Submissive & -0.076 & -0.07 & 0.03 & -2.43 & 0.015\\
Attitudes towards the war & -0.152 & -0.12 & 0.03 & -3.77 & <0.001\\
\addlinespace
Group-based moral shame & 0.36 & 0.22 & 0.05 & 4.63 & <0.001\\
Group-based image shame & 0.002 & 0 & 0.04 & 0.03 & 0.977\\
Group-based guilt & 0.033 & 0.02 & 0.03 & 0.76 & 0.450\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:TableS1}Path model predicting group-based guilt and shame from political beliefs.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{lrrrrr}
\toprule
\em{ } & \em{b} & \em{SE} & \em{Z} & \em{p} & \em{$\beta$}\\
\midrule
\em{\textbf{Guilt}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
Democratic values & 0.65 & 0.05 & 12.28 & <0.001 & 0.41\\
Political cynicism (politicians) & 0.1 & 0.05 & 2.15 & 0.032 & 0.09\\
Political cynicism (politics) & -0.03 & 0.05 & -0.69 & 0.492 & -0.03\\
Political alienation & 0.02 & 0.04 & 0.44 & 0.663 & 0.01\\
\addlinespace
Political responsibility & 0.1 & 0.05 & 2.19 & 0.028 & 0.07\\
\em{\textbf{Image shame}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
Democratic values & 0.64 & 0.05 & 12.13 & <0.001 & 0.4\\
Political cynicism (politicians) & 0.18 & 0.05 & 3.85 & <0.001 & 0.16\\
Political cynicism (politics) & -0.03 & 0.05 & -0.69 & 0.489 & -0.03\\
\addlinespace
Political alienation & -0.04 & 0.04 & -0.92 & 0.359 & -0.03\\
Political responsibility & 0.04 & 0.04 & 0.94 & 0.345 & 0.03\\
\em{\textbf{Moral shame}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}} & \em{\textbf{}}\\
Democratic values & 0.64 & 0.05 & 12.61 & <0.001 & 0.41\\
Political cynicism (politicians) & 0.2 & 0.04 & 4.52 & <0.001 & 0.18\\
\addlinespace
Political cynicism (politics) & -0.05 & 0.04 & -1.21 & 0.228 & -0.05\\
Political alienation & -0.06 & 0.04 & -1.53 & 0.125 & -0.05\\
Political responsibility & 0.05 & 0.04 & 1.3 & 0.195 & 0.04\\
\bottomrule
\end{tabular}
\end{table}
